A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-01 Main.Rmd
推敲 3070

---
title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica Neue} 
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
output:
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

```{r load, echo = F, message = F}
rm(list = ls())

evalFig <- T
if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
} else {
library(knitr)
}

opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.height = '500pixel', dpi = 100,
               message = FALSE, warning = FALSE, eval = T)
```

```{r Captions, eval = evalFig}
CapETRs <-
  "Fig. 1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown. The leaves grown under PSII-light "

CapEED <-
  "Fig. 2  The excitation balance between photosystems in response to wavelength of measuring light. "

@@

CapSPD <-
  "Fig. 4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight. The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey.<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
```

@@

EEDs <-
  EED_dat %>%
    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
    filter(wavelength > 400)  %>%
    replace_na(list(AlltoPSII = 0)) %>%
    ggplot(aes(x = wavelength, y = AlltoPSII)) +
    theme_bw2() +
    theme(panel.grid.major = element_blank()) +
    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
    gg_xy(c(380, 770, 0, 1.0)) +
    # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
    geom_line() +
    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
```

@@

Check terms:
level

@JIS_sunlight
------

**Abbreviations**
BR-light: blue + red LED light,
Chl: chlorophyll,
ETR: electron transport rate,
FR: far-red,
LED: light-emitting diode,
*P*~n~: net photosynthetic rate,
PFD: photon flux density,
PPFD: photosynthetic photon flux density,
PSI: photosystem I,
PSII: photosystem II,
SPD: relative spectral PFD distribution

@@

# How the interaction is generated? **(見出し軽すぎ)**

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
  When the excitation energy is in excess at PSII, the **energy distribution (この書き方は，いきなりだと知らない人にはわかりにくいものと思われる。)** to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
  In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Pfannschmidt_et_al2009AB; @Hogewoning_et_al2012PC].
  **This categorization is defined for a given leaf in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 kinds of monochromatic LED light as measuring light.
  **They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.**
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and the artificial sunlight (PSI-light) as measuring light.
  The risk of the biased evaluation by the use of BR-light for *P*~n~ measurements was clearly demonstrated.
  It was clearly demonstrated that the use of BR-light for *P*~n~ measurements could result in the biased evaluation.

  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 2).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

# Where the interaction should be concerned?

@@

  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Growth light provided by most of artificial light sources contains little FR light.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. XX).
  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].

  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. XX) and is namely PSI-light.
  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.

# How should net photosynthetic rate be measured?

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g. @Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight **(状況の限定)**.
  Note that the effect of the interaction seems to be less prominent than that of incident PPFD.
  **The measurements under *actual* sunlight, which usually causes a fluctuation in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.**
  The use of artificial light sources will mitigate the uncertainty caused by the fluctuation in the incident PPFD at the expense of the possible biases caused by the interaction.
  **This (明確に)** is because the SPDs of light from the artificial light sources are generally by far different from that of *in situ* light.
  To solve this dilemma between the *in situ* evaluation and the PPFD stability, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
  In both the prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.

  If the SPD of light that the leaves will be subject to is not predetermined, then the measurements should be made under several SPDs of light including PSII- and PSI-light.
  Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
  Therefore, the interaction should be tested so as not to make biased evaluation.
  If any the interaction, the results should be descriptively reported and should not be generalized.
  When the measurements were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.

@@

  The *P*~n~ under a single-level SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-levels of SPDs of measuring light so that the evaluation is not biased by the interaction.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
  In addition, measuring the *P*~n~ under multi-levels of SPDs is time-, resource-, and labor-consuming.
  Thus, these two approaches might not always be applied for evaluation of the leaf *P*~n~.
  At least in cases, measuements should be 少なくともできる場合には、努力すべきだ

@@

  The authors are grateful to Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for his kindness for 
  This work was supported by JSPS KAKENHI Grant Number 26·9372.

@@

```{r FigInteract, eval = evalFig, fig.cap = CapInteract}
InteractionView
```

```{r FigSPD, eval = evalFig, fig.width = 5, fig.height = 5, out.width = '500pixel', out.height = '500pixel'}
SPDs
```

# References

>>>>

```{r Captions, eval = evalFig}
CapEED <-
  "Fig. 1  The excitation balance between photosystems in response to wavelength of measuring light. The spectrum was calculated from the absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."

CapETRs <-
  "Fig. 2  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown. "

@@

CapSPD <-
  'Fig. 4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight. The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey. <sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
```

@@

EEDs <-
  EED_dat %>%
    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
    filter(wavelength > 400)  %>%
    replace_na(list(AlltoPSII = 0)) %>%
    ggplot(aes(x = wavelength, y = AlltoPSII)) +
    theme_bw2() +
    theme(panel.grid.major = element_blank()) +
    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
    gg_x(c(380, 770)) +
    # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
    geom_line() +
    scale_y_continuous(labels = c("0    ", "0.25", "0.50", "0.75", "1.00"),
                       breaks = c(0, 0.25, 0.5, 0.75, 1),
                       limits = c(0, 1.0),
                       expand = c(0, 0)) +
    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
```

@@

  The spectral photon flux density distributions (SPDs) of durign growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
  The plausible origin of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light are summarized.
  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend generalized characteristics.
  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.

**Abbreviations**
BR-light: blue and red LED light,
Chl: chlorophyll,
ETR: electron transport rate,
FR: far-red,
LED: light-emitting diode,
*P*~n~: net photosynthetic rate,
PFD: photon flux density,
PPFD: photosynthetic photon flux density,
PSI: photosystem I,
PSII: photosystem II,
SPD: relative spectral PFD distribution

@@

# A plausible origin of the interaction

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).

  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
  This categorization is defined for a given leaf in the relative scale, not in the absolute scale.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 2).
  **When the excitation energy is in excess at PSII, the fewer energy distributed to PSI results in the smaller photochemical reaction rate in PSI.**
  **This shortage in PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).**
  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  As a result of these resposes adjusting the EED, the excitation spectrum (Fig. XXX) differs depending on the SPD of grown light.
  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].

  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

# Some situations in which the interaction should be concerned

@@

  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Growth light provided by most of artificial light sources contains little FR light.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].

  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is namely PSI-light.
  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.

# Appropriate SPDs of measuring light for evaluating photosythetic rates

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  For instance, in case of evaluation of the transplants grown under artificial lighting [e.g. @Kozai2007POP] from the the prospective viewpoint, the measurements should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
  However, the measurements under sunlight might become uncertain due to fluctations in the incident PPFD.
  SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluation under a PPFD stable condition and to ensure the reproducibility and reliability of studies.
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.

  If the SPD of light that the leaves will be subject to is not predetermined, then the measurements should be made under several SPDs of light including PSII- and PSI-light.
  Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
  Therefore, the interaction should be tested so as not to make biased evaluation.
  If any the interaction, the results should be descriptively reported and should not be generalized.
  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.

@@

  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
  Although these two approaches might not always be applied for evaluation of the leaf *P*~n~, the interaction should be kept in mind to make circumspect conclusions.

@@

  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
  This work was supported by JSPS KAKENHI Grant Number 26·9372.

@@

```{r, eval = evalFig, fig.cap = CapInteract}
InteractionView
```

```{r, eval = evalFig, htmlcap = CapSPD}
SPDs
```

```{r, eval = evalFig, fig.cap = ""}
```
